Tracking $p$-adic precision

### 2014-02-26 padicprec.tex
Typos

\begin{proof}
We first remark that the functions $\Lambda(f)$ and $\NP(f)^\star$ 
are both left continuous. It is then enough to prove that they are
equal on a dense subset of $\R$. We are going to prove that they
coincide expect maybe on the set consisting of slopes of $\NP(f)$.

@@

\begin{proof}
It follows easily from Proposition \ref{prop:lambdaNP} and the fact that 
the slopes of the Legendre transform of a convex piecewise affine 
function $f$ are exactly the points where $f$ is not differentiable.
\end{proof}

@@

Note that sometimes the precision of a final result can be computed
a priori (using the methods of Section \ref{sec:differentials} for example).
Taking advantage of such knowledge can minimize artificial precision loss
even when using rougher precision types such as flat or jagged.
Separating precision from approximation also makes
it much easier to implement algorithms capable of processing different precision types,
since one can implement the arithmetic of the approximation separately from the logic
handling the precision.

>>>>

\begin{proof}
We first remark that the functions $\Lambda(f)$ and $\NP(f)^\star$ 
are both left continuous. It is then enough to prove that they are
equal on a dense subset of $\R$. We are going to prove that they
coincide except maybe on the set consisting of slopes of $\NP(f)$.

@@

\begin{proof}
It follows easily from Proposition \ref{prop:lambdaNP} and the fact that 
the slopes of the Legendre transform of a convex piecewise affine 
function $f$ are exactly the abscissae of the points where $f$ is not 
differentiable.
\end{proof}

@@

Note that sometimes the precision of a final result can be computed
a priori (using the methods of Appendix \ref{sec:differentials} for example).
Taking advantage of such knowledge can minimize artificial precision loss
even when using rougher precision types such as flat or jagged.
Separating precision from approximation also makes
it much easier to implement algorithms capable of processing different precision types,
since one can implement the arithmetic of the approximation separately from the logic
handling the precision.
